Sequence Specific Modeling of \emph{E.~coli} Cell-Free Protein Synthesis

### 2017-04-20 Paper_v1.tex
Some more small changes

\subsubsection{Potential Alternative Metabolic Optima}
Constraint based approaches can be used to compute alternative optimal solutions.
These solutions have the same objective value, e.g., productivity, but different underlying metabolic flux distributions.
Several techniques have been developed to estimate alternative optima, e.g., flux variability analysis \cite{Mahadevan2003264,Schuetz119} or mixed-integer approaches \cite{LEE2000711}.
In this study, we used reaction group flux variability analysis to estimate potential alternative optimal solutions for CAT production constrained by experimental measurements (Fig.~\ref{fig:norm}).
There were crucial pathways required for CAT production; for example, removal of the glycolysis/gluconoeogenesis or oxidative phosphorylation pathways resulted in no CAT production.
Likewise, there were also group knockouts that had no effect on productivity or the metabolic flux distribution, such as removal of isoleucine, leucine, and valine biosynthesis combined with histidine biosynthesis.
Globally, the constraint based simulation reached the same optimal CAT productivity for 40\% of the pairwise group knockouts, but had a different flux distribution when compared to the absence of knockouts.
For example, one of the features of the predicted optimal metabolic flux distribution was a high flux through the Entner-Douodoroff (ED) pathway.
Removal of the ED pathway had no effect on the CAT productivity compared to the absence of knockouts (Fig.~\ref{fig:norm}A).
Pairwise knockouts of the ED pathway and other subgroups (i.e. pentose phosphate pathway, cofactors, folate metabolism, etc.) also resulted in the same optimal CAT productivity.
However, there was a difference in the flux distribution with these knockouts (Fig.~\ref{fig:norm}B); thus, alternative optimal metabolic flux distributions exist for CAT production, despite experimental constraints.
In addition, knockouts of amino acid biosynthesis reactions had no effect on the productivity with the exception of ALA, ASP, ASN and GLU, GLN biosynthesis reactions, since amino acids were supplemented in the media.
ssFBA rerouted the metabolic flux to have the same productivity but an alterantive flux distribution (alternative optima), as can be seen for a pairwise knockout of GLY, SER biosynthesis with HIS biosynthesis (Fig.~\ref{fig:norm}B).
Ultimately, to determine the metabolic flux distribution occurring in CFPS, we need to add additional constraints to the flux estimation calculation.
For example, thermodynamic feasibility constraints may result in a better depiction of the flux distribution \cite{Henry:2007,Hamilton:2013},
and $^{13}$C labeling in CFPS could provide significant insight.
However, while $^{13}$C labeling techniques are well established for \emph{in~vivo} processes \cite{Zamboni:2009},
application of these techniques to CFPS remains an active area of research.
\begin{figure}[t!]
\includegraphics[width=1.0\textwidth]{./figs/Fig-7-FluxDistribution-Analysis.pdf}
\caption{The norm effect of pairwise knockouts of subgroups in the cell-free network (A) CAT productivity norm compared to no knockouts in the experimentally constrained case. (B) Flux distribution norm compared to no knockouts in the experimentally constrained case.}
\label{fig:norm}
\end{figure}

>>>>

\subsubsection{Potential Alternative Metabolic Optima}
Alternative optimal solutions have the same objective value, e.g., productivity, but different metabolic flux distributions.
Several techniques, e.g., flux variability analysis (FVA) \cite{Mahadevan2003264,Schuetz119} or mixed-integer approaches \cite{LEE2000711} can estimate alternative optima.
In this study, we used flux variability analysis to estimate potential alternative optimal solutions for CAT production constrained by experimental measurements (Fig.~\ref{fig:norm}).
FVA identified pathways required for CAT production; for example, deletion of the glycolysis/gluconoeogenesis or oxidative phosphorylation pathways resulted in no CAT production.
Likewise, there were pathway knockouts that had no effect on productivity or the metabolic flux distribution, such as removal of isoleucine, leucine, histidine and valine biosynthesis.
Globally, the constraint based simulation reached the same optimal CAT productivity for 40\% of the pairwise knockouts, but had different flux distributions compared with the absence of knockouts.
For example, one of the features of the predicted optimal metabolic flux distribution was a high flux through the Entner-Douodoroff (ED) pathway.
Removal of the ED pathway had no effect on the CAT productivity compared to the absence of knockouts (Fig.~\ref{fig:norm}A).
Pairwise knockouts of the ED pathway and other subgroups (i.e. pentose phosphate pathway, cofactors, folate metabolism, etc.) also resulted in the same optimal CAT productivity.
However, there was a difference in the flux distribution with these knockouts (Fig.~\ref{fig:norm}B); thus, alternative optimal metabolic flux distributions exist for CAT production, despite experimental constraints.
In addition, knockouts of amino acid biosynthesis reactions had no effect on the productivity with the exception of ALA, ASP, ASN and GLU, GLN biosynthesis reactions, since amino acids were supplemented in the media.
ssFBA rerouted the metabolic flux to have the same productivity but an alterantive flux distribution (alternative optima), as can be seen for a pairwise knockout of GLY, SER biosynthesis with HIS biosynthesis (Fig.~\ref{fig:norm}B).
Ultimately, to determine the metabolic flux distribution occurring in CFPS, we need to add additional constraints to the flux estimation calculation.
For example, thermodynamic feasibility constraints may result in a better depiction of the flux distribution \cite{Henry:2007,Hamilton:2013},
and $^{13}$C labeling in CFPS could provide significant insight.
However, while $^{13}$C labeling techniques are well established for \emph{in~vivo} processes \cite{Zamboni:2009},
application of these techniques to CFPS remains an active area of research.
\begin{figure}[t!]
\includegraphics[width=1.0\textwidth]{./figs/Fig-7-FluxDistribution-Analysis.pdf}
\caption{The norm effect of pairwise knockouts of subgroups in the cell-free network (A) CAT productivity norm compared to no knockouts in the experimentally constrained case. (B) Flux distribution norm compared to no knockouts in the experimentally constrained case.}
\label{fig:norm}
\end{figure}
